% -------------------------
% Resume in Latex
% ------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{4.35004pt} 



\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%% CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Jonathan Mark Allison} & Email : \href{mailto:mark.allison75@gmail.com}{mark.allison75@gmail.com}\\
                                                                                 & Mobile : +1(336)539-5573\\
\end{tabular*}


% -----------EXPERIENCE-----------------
\section{Experience} 
\resumeSubHeadingListStart

\resumeSubheading
{Nexient/NTT Data}{Haw River, NC}
{DevOps DevSecOps & Full-Stack Software Engineer}{June 2021 - Present}
\resumeItemListStart
  
  \resumeItem{In house project}
  {Migrate repos Azure Devops
    \begin{itemize}
      \item Encouraged cross-collabora on across teams during our migra on from on-prem to Azure cloud
      services. By further shortening me to market, our teams were be er able to deliver early, with be er
      quality products for our client.
      \item Assisted team with Pom ﬁles using maven to build ar facts in Azure Devops
    \end{itemize}
    \resumeItem{O'Reilly Auto}
    {Performed DevOps Engineer I role}
      \begin{itemize}
      \item Implemented mul -environment pla orm deployment for Dev/QA/Test/Perf/Prod/DR in
      Azure/ADO using Terraform/Terragrunt.
      \item Used Packer to create system images.
      \item git
      \item Managed SE Linux rules to allow apps to run while setenforce = true.
      \item Veriﬁed code was working with Terratest, and Ruby spec tests.
      \item Implemented post deploy system conﬁg using bash script.
      \item Installed Crowdstrike and Nessus using Ansible.
      \item Tested security in applica ons using Snyk
      \item Applied TFLint to repos for errors before submitting
      \item Applied TFLint to repos for errors before submi ng
    \end{itemize}

  }
      
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Freelance Web Developer}{Haw River, NC}
{Proteus Themes}{October 2020 - Present}
\resumeItemListStart
  \resumeItem{Customer Service}
  {Responsive to customers needs

    \begin{itemize}
      \item Respond to questions from customers who submit tickets about their WordPress Themes
      \item Maintain JavaScript and CSS for WordPress themes
     
    \end{itemize}
  }
  \resumeItemListEnd
\resumeSubHeadingListEnd

  

\resumeSubHeadingListStart
\resumeSubheading
{Pilot Flying J}{Graham, NC}
{Lead Maintenance}{Oct 2014 - Oct 2019}
\resumeItemListStart
  \resumeItem{Discover}
  {Coordinated ac vi es with other departments to ensure that services are provided in an
  eﬃcient and mely manner

    \begin{itemize}
      \item Managed a staﬀ of 10 employees. Tasks included leading 1:1 mee ngs, assigning daily
      tasks(Safety checks, checking the grounds, and store cleanliness) and employee schedules
      for work
      
    \end{itemize}

  }

 
      
  \resumeItemListEnd
  \resumeSubHeadingListEnd


 


  % --------PROGRAMMING SKILLS------------
  \section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{:  Docker, Kubernetes, GoLang, Git, Linux, Ansible, Terraform,
      Terragrunt, Packer Images, Terratest, Agile, Jira, Nessus, Crowdstrike, Snyk, TFLint, Groovy,
      HTML, CSS, LESS/SASS, Javascript, React, Redux, Express, NodeJS, Jest, SQLite3, Python}
        \hfill
      \textbf{Technologies}{: AWS, Azure, Azure Devops, Jenkins}
    }
  \resumeSubHeadingListEnd

  % -----------EDUCATION-----------------
  \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Lambda School}{Silicon Valley, California}
  {Full Stack Web Development & Computer Science}{Oct.2019 -- Aug.2020}
  \resumeSubHeadingListEnd

  % ------------References----------------
  \section{References}
  Available upon request.

  % -------------------------------------------
\end{document}
